Data Preparation, Integration and Cleaning

### 2017-02-05 abbDataPrep_Script.Rmd
start analysis script

@@

  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, beach.shp, core.suburbs,
       exch.rate, ltr.col, str.col, sa1s.shp, suburbs.shp, study.suburbs,
       file=paste0(data.path, 'prepared/prep_workspace.RData'))
```

>>>>

  ## Remove those with less than 180 observed days (missing obs)
  str.data <- str.data[str.data$total.days >= 180, ]

@@

  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, 
       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
       suburbs.shp, study.suburbs,
       file=paste0(data.path, 'prepared/prep_workspace.RData'))
